Assessment of the ability to track changes for nowcasts, measurements, and forecasts

### 2024-04-10 paper.tex
Update on Overleaf.

\abstract{
Measurements, nowcasts, and forecasts aim to indicate a value of interest's change through direction and magnitude.
The direction of change alone is easily and intuitively interpretable information on the development and can be an early sign of regime switching.
We refer to a measurement's, nowcast's, or forecast's ability to predict the right direction of development as the ability to track changes.
We present techniques to assess this ability as accompanying evaluation in all application areas, including quantitative measures.
We provide extensions for noisy data and estimation uncertainty using bootstrap confidence intervals and exclusion areas.
We review and present new visualization techniques to assess the local ability to track changes and enlarge the scope to probabilistic nowcasts and forecasts.
We exemplify the methods for three medical or healthcare problems: COVID-19-nowcasting, emergency department arrival forecasting, and invasive and non-invasive blood pressure measurements.
}

>>>>

\abstract{ % Weniger We; Erste zwei Sätze kombinieren
In addition to the numerical precision, the direction of change alone is easily and intuitively interpretable information on the development.
We consider whether measurements, nowcasts, and forecasts are able to correctly indicate the direction of change of a value of interest.
We refer to the ability to predict the right direction of development as the ability to track changes.

We present techniques to assess this ability as accompanying evaluation in all application areas, including quantitative measures.
We provide extensions for noisy data and estimation uncertainty using bootstrap confidence intervals and exclusion areas.
We review and present new visualization techniques to assess the local ability to track changes and enlarge the scope to probabilistic nowcasts and forecasts.
We exemplify the methods for three medical or healthcare problems: COVID-19-nowcasting, emergency department arrival forecasting, and invasive and non-invasive blood pressure measurements.
}
